\mireval{}

### 2014-05-09 paper/paper.tex
Switching footnote to ref and adding ref to comparison

Based on this representation, we can symbolically define our interpretation of the five rules used in MIREX 2013\footnote{http://www.music-ir.org/mirex/wiki/2013:Audio\_Chord\_Estimation} to compare an estimated chord $\mathcal{C}_{est}$ with a reference $\mathcal{C}_{ref}$.
\textbf{Root} is given by $\mathcal{R}_{est} == \mathcal{R}_{ref}$, for all chords.
\textbf{Major-Minor} includes \textbf{Root}, plus $\mathcal{S}_{est} == \mathcal{S}_{ref}$ subject to $\mathcal{S}_{ref} \in \{Maj, min\}$.
\textbf{Major-Minor-Inv} includes \textbf{Major-minor}, plus $\mathcal{B}_{est} == \mathcal{B}_{ref}$ subject to $\mathcal{B}_{ref} \in \mathcal{S}_{ref}$.
\textbf{Sevenths} follows \textbf{Major-minor}, but is instead subject to $\mathcal{S}_{ref} \in \{Maj, min, Maj7, min7, 7, minmaj7\}$.
Finally, \textbf{Sevenths-Inv} includes \textbf{Sevenths}, plus $\mathcal{B}_{est} == \mathcal{B}_{ref}$ subject to $\mathcal{B}_{ref} \in \mathcal{S}_{ref}$.
Before proceeding, we draw attention to the set-inclusion conditions above, e.g. ``subject to...'', meaning that a comparison is \emph{ignored} during evaluation if the given criteria is not satisfied.

@@

\subsection{Weighted Chord Symbol Recall}
The non-negligible average relative changes seen in the chord metrics are caused by two main sources of ambiguity.
%Some interval mappings aren't well-defined.
First, we find some chord labels in the MIREX reference annotations lack well-defined, i.e. singular, mappings into a comparison space. 
One such example is $D:maj(*1)/\#1$.
While the quality shorthand indicates ``major'', the asterisk implies the root is omitted and thus it is unclear whether $D:maj(*1)/\#1==D:maj1$.
%Some chords get dropped in different scenarios, and we can't replicate the logic. 
Second, and more importantly, such chords are likely ignored during evaluation, and we are unable to replicate the exact exclusion logic used by MIREX. 
This has proven to be particularly difficult in the two inversion rules, and manifests in Table \ref{tab:comparison}. 
For example, it seems as though $Bb:maj(9)/9$ was \emph{not} excluded from the MIREX evaluation, contradicting the description provided online.
This chord alone causes an observable difference between the results of our implementation and previously reported results.

>>>>

Based on this representation, we can symbolically define our interpretation of the five rules used in MIREX 2013\cite{choi2013mirex} to compare an estimated chord $\mathcal{C}_{est}$ with a reference $\mathcal{C}_{ref}$.
\textbf{Root} is given by $\mathcal{R}_{est} == \mathcal{R}_{ref}$, for all chords.
\textbf{Major-Minor} includes \textbf{Root}, plus $\mathcal{S}_{est} == \mathcal{S}_{ref}$ subject to $\mathcal{S}_{ref} \in \{Maj, min\}$.
\textbf{Major-Minor-Inv} includes \textbf{Major-minor}, plus $\mathcal{B}_{est} == \mathcal{B}_{ref}$ subject to $\mathcal{B}_{ref} \in \mathcal{S}_{ref}$.
\textbf{Sevenths} follows \textbf{Major-minor}, but is instead subject to $\mathcal{S}_{ref} \in \{Maj, min, Maj7, min7, 7, minmaj7\}$.
Finally, \textbf{Sevenths-Inv} includes \textbf{Sevenths}, plus $\mathcal{B}_{est} == \mathcal{B}_{ref}$ subject to $\mathcal{B}_{ref} \in \mathcal{S}_{ref}$.
Before proceeding, we draw attention to the set-inclusion conditions above, e.g. ``subject to...'', meaning that a comparison is \emph{ignored} during evaluation if the given criteria is not satisfied.

@@

\subsection{Weighted Chord Symbol Recall}
The non-negligible average relative changes seen in the chord metrics are caused by two main sources of ambiguity.
%Some interval mappings aren't well-defined.
First, we find some chord labels in the MIREX reference annotations lack well-defined, i.e. singular, mappings into a comparison space. 
One such example is $D:maj(*1)/\#1$.
While the quality shorthand indicates ``major'', the asterisk implies the root is omitted and thus it is unclear whether $D:maj(*1)/\#1==D:maj1$.
%Some chords get dropped in different scenarios, and we can't replicate the logic. 
Second, and more importantly, such chords are likely ignored during evaluation, and we are unable to replicate the exact exclusion logic used by MIREX \cite{choi2013mirex}.
This has proven to be particularly difficult in the two inversion rules, and manifests in Table \ref{tab:comparison}. 
For example, it seems as though $Bb:maj(9)/9$ was \emph{not} excluded from the MIREX evaluation, contradicting the description provided online.
This chord alone causes an observable difference between the results of our implementation and previously reported results.
